The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-10-10 paper.qmd
fixed variance formula

@fig-data shows the first six rows and the geographical boundaries of our data set. 
The temperature variable was generated using a sine wave, that is $Temperature_i = 29-3\cdot{|Latitude_i - \sin{2 \cdot Longitude_i}|}$ where the $Longitude$ and $Latitude$ are the longitude and latitude of the county's centroid scaled to a standard normal distribution. 
Each county's variance is independently, randomly sampled from a uniform distribution. 
The low standard errors are drawn from a $U_{[0,1]}$ distribution, while the high standard errors are drawn from a $U_{[1,2]}$ distribution. 
As we are dealing with an average, the sampling distribution would be approximately normal by the central limit theorem, so each county temperature estimate is assumed to come from a $N(Temp_i, SE_{case,i})$. 
This is the data we will be using in our spatial uncertainty examples for the rest of the paper.

>>>>

@fig-data shows the first six rows and the geographical boundaries of our data set. 
The temperature variable was generated using a sine wave, that is $Temperature_i = 29-2\cdot{|Latitude_i - \sin{2 \cdot Longitude_i}|}$ where the $Longitude$ and $Latitude$ are the longitude and latitude of the county's centroid scaled to a standard normal distribution. 
Each county's variance is independently, randomly sampled from a uniform distribution. 
The low standard errors are drawn from a $U_{[0,1]}$ distribution, while the high standard errors are drawn from a $U_{[1,2]}$ distribution. 
As we are dealing with an average, the sampling distribution would be approximately normal by the central limit theorem, so each county temperature estimate is assumed to come from a $N(Temp_i, SE_{case,i})$. 
This is the data we will be using in our spatial uncertainty examples for the rest of the paper.
